\chapter*{Preface}
% from http://www.hpmor.com/chapter/1
% merged and edited with additional author comments from http://www.hpmor.com/chapter/22
% This is not a strict single-point-of-departure fic—there exists a primary point of departure, at some point in the past, but also other alterations. The best term I’ve heard for this fic is “parallel universe”.

I am happy to have written this book for you,\\
and I am honored that you read it.\\
Many of you have declared yourselves my friends,\\
and that knowledge is shining warmly inside me.
~

This is a rationalist story; its mysteries are solvable, and meant to be solved. The text contains many clues: obvious clues, not-so-obvious clues, truly obscure hints which I was shocked to see some readers successfully decode, and massive evidence left out in plain sight. 
The pacing of the story is that of serial fiction, i.e., that of a TV show running for a predetermined number of seasons, whose episodes are individually plotted but with an overall arc building to a final conclusion.

% The story has been corrected to British English up to Ch. 17, and further Britpicking is currently in progress (see the /HPMOR subreddit).

All science mentioned is real science. But please keep in mind that, beyond the realm of science, the views of the characters may not be those of the author. Not everything the protagonist does is a lesson in wisdom, and advice offered by darker characters may be untrustworthy or dangerously double-edged.
What warm!Harry thinks is \emph{often} meant as a good pattern to follow, especially if Harry thinks about how he can cite scientific studies to back up a particular principle. But not everything Harry does or thinks is a good idea. That wouldn’t work as a story. And the less warm characters may sometimes have valuable lessons to offer, but those lessons may also be dangerously double-edged.

Thank you very much to all my reviewers. (Especially Darkandus on Viridian Dreams, for the surprisingly inspiring comment "Lungs and tea are not meant to interact").

If you haven’t visited \url{https://hpmor.com}, don’t forget to do that at some point; otherwise you'll miss out on the fan art, how to learn everything Harry knows, and more. If you don’t just enjoy this fic, but learn something from it, then please consider sharing it. A work like this only does as much good as there are people who read it.

I wish for you to live long, and prosper\\
EXPECTO PATRONUM!

— Eliezer Yudkowsky

\chapter*{Notes on the Text}

This story was originally published in serial format by Eliezer Yudkowsky on FanFiction.net under the alias Less Wrong, running from February 2010 to March 2015. 
In preparing the present edition, a few decisions were made to
balance conflicting interests: preserving the character of the fan fiction as
it was published, and adapting the text to a form more appropriate for a
printed book.

The 660,000-word text is divided into six books, as suggested by the author, as were the titles
(except for Book 2, which the Editor of this edition has take the liberty of giving a more badass name than "The Professor's Games").
This edition from chapter 5 onward is based primarily on
the official text maintained by Reuben Thomas on Github (ver. 1.2.12, June 2024),
with additional edits by Eryn Hopps and by the Editor.
The first four chapters have been replaced by an edited version of Daystar Eld's "Remix of Rationality" (so named by Yudkowsky),
a fan edit intended to smooth out the tonal and characterization differences between those early chapters and later portions of the work.
The Remix incorporated here was originally edited by Xenohedron in 2015 to conform more closely with Yudkowsky's original text and style,
with minor fixes to punctuation and the like in 2018. Further edits to those four chapters were made by the Editor,
mostly "Britpicks" implementing British spelling and vocabulary in line with the following chapters
(which themselves were mostly Britpicked by others over the years since the chapters were originally released).
This Editor is also indebted to Jeremie Knuesel for certain layout fixes,
and to Ian Storm Taylor, Lily Yao Lu, and ForeChin99 for elements of the cover design.

As originally serialized, many of the chapters began with an author's note and/or epigraph quoting from the chapter itself;
they are removed from this edition. 
Chapter 113 originally included a "final exam" inviting reader participation; that likewise is removed.
Also removed are two chapters of non-canonical \emph{omake}
(chapters 11 and 64) in which the author tries his hand at parody lyrics, plays with alternate endings, and briefly considers
what rationalism would do in places like Middle Earth, Equestria, or Agrabah.
While fun, those chapters likewise disrupted the novelistic flow and are left as an online exercise for true HPMOR fanatics. 
The remaining chapters of the respective books have been renumbered accordingly.

I originally undertook to print a single copy of this book for myself after devouring it for the third time,
mostly on small device screens.
But it quickly occurred to me that I know at least one other person who would appreciate a story of rationality triumphant.
Jeff, my brother in law and in spirit: may this book bring you joy, knowledge, and hope for the deep future.

— Jonathon Bashford

%  LocalWords:
